### 2017-10-27 tex/article.tex
texfile to git, plot export in evaluate + added article.tex to git repo + added export as .eps to the plots in evaluate.ipynb

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Journal Article
% LaTeX Template
% Version 1.4 (15/5/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com) with extensive modifications by
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
%for images

% /\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\
%
% THIS IS IMPORTANT! RUN WITH pdflatex -shell-escape TO AVOID EPS CONVERSION ERROR
%
% /\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\

\documentclass[twoside,twocolumn]{article}

\usepackage{graphicx}

\graphicspath{ {../img/} }

\usepackage{subfig}

\usepackage{blindtext} % Package to generate dummy text throughout this template

\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.05} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics

\usepackage[english]{babel} % Language hyphenation and typographical rules

\usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
\usepackage[labelfont={bf,up},textfont={it,up}]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables

\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text

\usepackage{enumitem} % Customized lists
\setlist[itemize]{noitemsep} % Make itemize lists more compact

\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

\usepackage{titlesec} % Allows customization of titles
\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
\renewcommand\thesubsection{\roman{subsection}} % roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large}{\thesubsection.}{1em}{} % Change the look of the section titles

\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Running title $\bullet$ May 2016 $\bullet$ Vol. XXI, No. 1} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text

\usepackage{titling} % Customizing the title section

\usepackage{hyperref} % For hyperlinks in the PDF

\usepackage{amssymb,amsmath,bbold,braket}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\setlength{\droptitle}{-4\baselineskip} % Move the title up

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{Simulating a flock of birds} %Simulating a flock of birds
\author{%
\textsc{Steffen Randrup, Michel Smola, Andrei Timus}\thanks{A thank you or further information} \\[1ex] % Your name
\normalsize University of Copenhagen \\ % Your institution
%\normalsize \href{mailto:john@smith.com}{john@smith.com} % Your email address
%\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
%\textsc{Jane Smith}\thanks{Corresponding author} \\[1ex] % Second author's name
%\normalsize University of Utah \\ % Second author's institution
%\normalsize \href{mailto:jane@smith.com}{jane@smith.com} % Second author's email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%
\begin{abstract}
\noindent %\blindtext % Dummy abstract text - replace \blindtext with your abstract text

In this paper we present a model for studying the behaviour of a group of particles which have some level of interaction between them. The model was inspired from the $[1]$ paper and as in$ [1]$ the particles have a constant absolute velocity and at each time step  assume the average direction of nearby neighbours with some added perturbation, $\eta$. The behaviour was studied by analysing how the average velocity of the flock $v_a$ varied when parameters like noise, density, number of particles where changed. In addition to $[1]$ we have introduced a cone of vision for every particle and studied the behaviour of the flock in the same conditions. From the simulation results it has been observed that the flock goes through a phase transition where all the particles assume the same direction. The average velocity $v_a$ played the role of an order parameter and it scaled with $(\eta_c-\eta)^\beta$, where $\beta$ is a critical exponent.

\end{abstract}
}

%----------------------------------------------------------------------------------------

\begin{document}

% Print the title
\maketitle

%----------------------------------------------------------------------------------------
%	ARTICLE CONTENTS
%----------------------------------------------------------------------------------------

\section{Introduction}

%\lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
%\blindtext % Dummy text

%\blindtext % Dummy text

%------------------------------------------------

The particles where distributed randomly in a square lattice of size L. Each particle had assigned a random direction $\theta$ and a constant interaction radius r. One update consisted in modifying the position of all particles according to the following equation:

\begin{equation}
x_{i}(t+1)=x_i(t)+v_i(t)\Delta t
\end{equation}
where $\Delta$t represents the time between 2 updates.
The velocity of a particle had a constant absolute value and a direction given by:
\begin{equation}
\theta(t+1)=\braket{\theta(t)}_r+\Delta \theta
\end{equation}

where 
\begin{equation}
\braket{\theta(t)}_r=artan\frac{\braket{sin(\theta(t))}_r}{\braket{cos(\theta(t))}_r}
\end{equation}
is the average direction of the velocities of nearby particles wich are inside the influence circle of radius r of the given particle.$\Delta$t represents the noise in the system and takes values with equal probability within the interval $[-\eta/2,\eta/2]$. For a constant number of particles there are 3 parameters which can be varied: $\eta$,$\rho$,and v, where v is the distance a particle travels between 2 updates.
\begin{figure}[!htb]
	\centering
	\subfloat{{\includegraphics[width=2cm]{test1}}}
	\subfloat{{\includegraphics[width=2cm]{test2}}}
	\qquad
	\subfloat{{\includegraphics[width=2cm]{test2}}}
	\subfloat{{\includegraphics[width=2cm]{test2}}}
	\caption{test for figures}
\end{figure}

Figure 1 shows the configuration of birds for different values of rho and eta. ..........................
..................................

If the density is high enough, while the noise has low values, the system goes through a kinetic phase transition where all the particles share the same direction. In order to study this behaviour we have determined the average normalized velocity of the system and investigated how it changes when certain parameters are modified:
\begin{equation}
v_a=\frac{1}{Nv}\mid\sum_{i=1}^{N} v_i\mid
\end{equation}
For the disordered phase $v_a$ is aproximatively 0, while for the ordered phase $v_a$ has the value of 1.
%rephrase:
In the following figure we show how $v_a$ varies with the noise $\eta$ and density  $\rho$ for a constant value of density and noise respectively.As it can be seen from the graph the overall alignment of the particles depends on the noise and for a high number of particles N the system becomes more disordered. 
%
\begin{figure}[!htb]
	\centering
	\subfloat{{\includegraphics[width=6cm]{va_over_rho}}}

	\subfloat{{\includegraphics[width=6cm]{density}}}
	\caption{test for figures}
\end{figure}

The behaviour of $v_a$ is found to be similar to that of the order parameter of some equilibrium systems close to their critical point. For large system sizes the data shows scaling which is an indication of a phase transition. Therefore it's possible to describe the behaviour of $v_a$ in the thermodynamic limit using the following equations:
\begin{equation}
v_a \approx[\eta_c(\rho)-\eta]^\beta 
\end{equation}
\begin{equation}
v_a \approx[\rho-\rho_c(eta)]^\gamma
\end{equation}

\begin{figure}[!htb]
	\centering
	\subfloat{{\includegraphics[width=6cm]{criticaleta}}}

	\caption{test for figures}
\end{figure}

\section{Results}

Maecenas sed ultricies felis. Sed imperdiet dictum arcu a egestas. 
\begin{itemize}
\item Donec dolor arcu, rutrum id molestie in, viverra sed diam
\item Curabitur feugiat
\item turpis sed auctor facilisis
\item arcu eros accumsan lorem, at posuere mi diam sit amet tortor
\item Fusce fermentum, mi sit amet euismod rutrum
\item sem lorem molestie diam, iaculis aliquet sapien tortor non nisi
\item Pellentesque bibendum pretium aliquet
\end{itemize}
\blindtext % Dummy text

Text requiring further explanation\footnote{Example footnote}.

%------------------------------------------------

\section{Results}

\begin{table}
\caption{Example table}
\centering
\begin{tabular}{llr}
\toprule
\multicolumn{2}{c}{Name} \\
\cmidrule(r){1-2}
First name & Last Name & Grade \\
\midrule
John & Doe & $7.5$ \\
Richard & Miles & $2$ \\
\bottomrule
\end{tabular}
\end{table}

\blindtext % Dummy text

\begin{equation}
\label{eq:emc}
e = mc^2
\end{equation}

\blindtext % Dummy text

%------------------------------------------------

\section{Discussion}

\subsection{Subsection One}

A statement requiring citation \cite{Figueredo:2009dg}.
\blindtext % Dummy text

\subsection{Subsection Two}

\blindtext % Dummy text

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

\bibitem[Figueredo and Wolf, 2009]{Figueredo:2009dg}
Figueredo, A.~J. and Wolf, P. S.~A. (2009).
\newblock Assortative pairing and life history strategy - a cross-cultural
  study.
\newblock {\em Human Nature}, 20:317--330.

\end{thebibliography}

%----------------------------------------------------------------------------------------

\end{document}

### 2017-10-28 src/birds.py
frame by frame

@@ -52,8 +52,8 @@ class Flock:
 
         # check if viewing-angle (theta_velocity) +- angle_view/2 matches distance-vector to neighbors (theta(pos1-pos2))
         if self.angle_view:
-            mask *= np.absolute(np.arctan2(self.dy.T, self.dx.T) - np.arctan2(self.velocity[:,1],self.velocity[:,0])) < self.angle_view
-            # mask *= np.divide( self.dx.T * self.velocity[:,0] + self.dy.T * self.velocity[:,1], self.distance, np.ones_like(self.distance), where=self.distance!=0) > np.cos(self.angle_view)
+            #mask *= np.absolute(np.arctan2(self.dy.T, self.dx.T) - np.arctan2(self.velocity[:,1],self.velocity[:,0])) < self.angle_view
+            mask *= np.divide( self.dx.T * self.velocity[:,0] + self.dy.T * self.velocity[:,1], self.distance, np.ones_like(self.distance), where=self.distance!=0) > np.cos(self.angle_view)
 
 
         mask_count = np.maximum(mask.sum(axis=1), 1).reshape(self.args["n"],1)
@@ -164,6 +164,8 @@ def update(*args):
     collection.update()
 
 
+
+
 defaults = {
     "angle": 0,
     "v": 0.03,
@@ -259,6 +261,8 @@ if __name__ == '__main__':
     else:
         param_record = False
 
+    interval = 10 if args.fps==defaults["fps"] else 1000/args.fps
+
     if not args.batch:
         if args.export:
             animation = FuncAnimation(fig, update, interval=10, frames=args.frames)
@@ -267,7 +271,7 @@ if __name__ == '__main__':
                        metadata={'artist': 'Nicolas P. Rougier'})
 
         else:
-            animation = FuncAnimation(fig, update, interval=10, frames=args.frames, repeat=not args.out)
+            animation = FuncAnimation(fig, update, interval=interval, frames=args.frames, repeat=not args.out)
             plt.show()
 
     if args.out:

### 2017-10-28 src/birds.py
small changes

@@ -20,8 +20,8 @@ class Flock:
 
         # randomly distributed starting velocities, might come out pretty much the same as if you just set self.velocity = np.zeros((n,2),dtype=np.float32) but avoids division by zero.
         angles = np.random.uniform(0,2*np.pi,self.args["n"])
-        self.velocity = (np.array([np.cos(angles),np.sin(angles)])*self.args["v"]).astype(np.float32).T
-        self.position = np.random.rand(n,2).astype(np.float32)*[self.args["width"],self.args["height"]]
+        self.velocity = (np.array([np.cos(angles),np.sin(angles)])*self.args["v"]).astype(np.float64).T
+        self.position = np.random.rand(n,2).astype(np.float64)*[self.args["width"],self.args["height"]]
 
         # test boid configuration
         if n<=3:
@@ -41,8 +41,8 @@ class Flock:
     def get_va(self):
         n = self.args["n"]
         if self.args["v"]:
-            vges = np.sum(self.velocity,axis=0)
-            return 1/(n*self.args["v"]) * np.sqrt((vges*vges).sum())
+            vsum = np.sum(self.velocity,axis=0)
+            return 1./(n*self.args["v"]) * np.sqrt((vsum*vsum).sum())
 
     def run(self):
         n = self.args["n"]
@@ -220,7 +220,7 @@ if __name__ == '__main__':
     parser.add_argument("--export", "-e", help="Export video file and exit", action="store_true")
     parser.add_argument("--frames", help="Number of frames for export to video or parameter record file, default="+str(defaults["frames"]), type=int, default=defaults["frames"])
     parser.add_argument("--vfile", help="Out-File for video export, default="+str(defaults["vfile"]), type=str, default=defaults["vfile"])
-    parser.add_argument("--fps", help="Set Video Framerate for export, default="+str(defaults["fps"]), type=int, default=defaults["fps"])
+    parser.add_argument("--fps", help="Set Video Framerate for playback/export, default="+str(defaults["fps"]), type=int, default=defaults["fps"])
     parser.add_argument("--scale", "-s", help="Scale field size, radius, v, default="+str(defaults["scale"]), type=float, default=defaults["scale"])
     parser.add_argument("--rho", help="Set constant density and calculate L from n and rho", type=float)
     parser.add_argument("--out", "-o", help="Specify output File for recording Parameters, Filetype: .npz", type=str)
@@ -265,7 +265,7 @@ if __name__ == '__main__':
 
[…]

### 2017-10-28 tex/article.tex
Wrote some results and discussion

@@
 
+\usepackage{todonotes}
+
 \usepackage{blindtext} % Package to generate dummy text throughout this template
@@
 \fancyfoot{} % Blank out the default footer
-\fancyhead[C]{Running title $\bullet$ May 2016 $\bullet$ Vol. XXI, No. 1} % Custom header text
+\fancyhead[C]{Bird simulation $\bullet$ \today $\bullet$ v1} % Custom header text
 \fancyfoot[RO,LE]{\thepage} % Custom footer text
@@
 \author{%
-\textsc{Steffen Randrup, Michel Smola, Andrei Timus}\thanks{A thank you or further information} \\[1ex] % Your name
+\textsc{Steffen Randrup, Michel Smola, Andrei Timus}\\[1ex] % Your name
 \normalsize University of Copenhagen \\ % Your institution
@@
 In this paper we present a model for studying the behaviour of a group of particles which have some level of interaction between them.
-The model was inspired from the $[1]$ paper and as in$ [1]$ the particles have a constant absolute velocity and at each time step  assume the average direction of nearby neighbours with some added perturbation, $\eta$.
+The model was inspired from the~\cite{Vicsek} paper\todo{Present paper and author by name.
+Also it probably shouldn't be in the abstract} and as in~\cite{Vicsek} the particles have a constant absolute velocity and at each time step  assume the average direction of nearby neighbours with some added perturbation, $\eta$.
 The behaviour was studied by analysing how the average velocity of the flock $v_a$ varied when parameters like noise, density, number of particles where changed.
@@
 
-%\lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
-%\blindtext % Dummy text
-
-%\blindtext % Dummy text
-
-%------------------------------------------------
-
 The particles where distributed randomly in a square lattice of size L.
@@
 \begin{equation}
-\braket{\theta(t)}_r=artan\frac{\braket{sin(\theta(t))}_r}{\braket{cos(\theta(t))}_r}
+\braket{\theta(t)}_r=\arctan\frac{\braket{sin(\theta(t))}_r}{\braket{cos(\theta(t))}_r}
 \end{equation}
@@
 	\centering
-	\subfloat{{\includegraphics[width=2cm]{test1}}}
-	\subfloat{{\includegraphics[width=2cm]{test2}}}
+	\subfloat{{\includegraphics[width=\columnwidth/2]{test1}}}
+  \subfloat{{\includegraphics[width=\columnwidth/2]{test2}}}
 	\qquad
-	\subfloat{{\includegraphics[width=2cm]{test2}}}
-	\subfloat{{\includegraphics[width=2cm]{test2}}}
+	\subfloat{{\includegraphics[width=\columnwidth/2]{test2}}}
+	\subfloat{{\includegraphics[width=\columnwidth/2]{test2}}}
 	\caption{test for figures}
+  \label{fig:configs}
 \end{figure}
 
-Figure 1 shows the configuration of birds for different values of rho and eta. ..........................
-..................................
+Figure~\ref{fig:configs} shows the configuration of birds for different values of rho and eta.
 
@@
 \begin{equation}
-v_a=\frac{1}{Nv}\mid\sum_{i=1}^{N} v_i\mid
+v_a=\frac{1}{Nv}\left\vert\sum_{i=1}^{N} v_i\right\vert
 \end{equation}
 For the disordered phase $v_a$ is aproximatively 0, while for the ordered phase $v_a$ has the value of 1.
-%rephrase:
-In the following figure we show how $v_a$ varies with the noise $\eta$ and density  $\rho$ for a constant value of density and noise respectively.As it can be seen from the graph the overall alignment of the particles depends on the noise and for a high number of particles N the system becomes more disordered.
-%
-\begin{figure}[!htb]
-	\centering
-	\subfloat{{\includegraphics[width=6cm]{va_over_rho}}}
-
-	\subfloat{{\includegraphics[width=6cm]{density}}}
-	\caption{test for figures}
-\end{figure}
+\todo{refrace}
 
@@
 Therefore it's possible to describe the behaviour of $v_a$ in the thermodynamic limit using the following equations:
+\todo[inline]{This needs to be much clearer. It is not obvious how this behaviour is similar or why it's reasonable to assume it would be}
+
 \begin{equation}
+  \label{eq:va-eta}
   v_a \approx[\eta_c(\rho)-\eta]^\beta 
@@
 \begin{equation}
+  \label{eq:va-rho}
   v_a \approx[\rho-\rho_c(eta)]^\gamma
@@
 
-\begin{figure}[!htb]
-	\centering
-	\subfloat{{\includegraphics[width=6cm]{criticaleta}}}
-
-	\caption{test for figures}
-\end{figure}
+We further extend the model by implementing a cone-like vision.
+This means, that rather than averaging the velocities over all birds within a certian radius, we only look at a slice of this circle.
+For a bird to be within the vision of another bird, it must be within the interaction radius, $r$, and the angle between the birds velocities must be within $\pm \theta_{cone}$.
+In the limit $\theta_{cone} = 180 \deg$\todo{use radians for paper?} we should see the same behavior of the model as without implementation of this vision.
 
@@
 
-Maecenas sed ultricies felis. Sed imperdiet dictum arcu a egestas. 
-\begin{itemize}
-\item Donec dolor arcu, rutrum id molestie in, viverra sed diam
-\item Curabitur feugiat
-\item turpis sed auctor facilisis
-\item arcu eros accumsan lorem, at posuere mi diam sit amet tortor
-\item Fusce fermentum, mi sit amet euismod rutrum
-\item sem lorem molestie diam, iaculis aliquet sapien tortor non nisi
-\item Pellentesque bibendum pretium aliquet
-\end{itemize}
-\blindtext % Dummy text
+The alignment, $v_a$, depends on the amount of randomness, $\eta$, in the system and the density, $\rho$, as seen in equations~\eqref{eq:va-eta} and \eqref{eq:va-rho}.
+In Figure\ref{fig:va_over_eta} we see how, the alignment of the birds decreases as the randomness of their motion increases.
+The decrease is to be expected as a higher degree of randomness should disrupt alignment.
+What might be more interesting is the general shape of the curves.
+We may then determine $\beta$ from equation\eqref{eq:va-eta} to be \todo{get value of $\beta$} \todo{What do we use $\beta$ for?}.
+This is also shown in figure~\ref{fig:criticaleta}.
+The results presented here are all computed without the conevision (or with $\theta_{cone} = 180\deg$)\todo{use radians for paper?}.
+The effects of it will be presented in \ref{subsec:results_conevision}.
 
-Text requiring further explanation\footnote{Example footnote}.
+\begin{figure}[!htb]
+  \centering
+  \includegraphics[width=\columnwidth]{va_over_eta}
+  \caption{Dependance of alignment on randomness}
+  \label{fig:va_over_eta}
+\end{figure}
 
-%------------------------------------------------
+\begin{figure}[!htb]
+	\centering
+	\includegraphics[width=\columnwidth]{va_over_etac_minus_eta_over_etac}
+	\caption{Determining $\beta$}
+  \label{fig:criticaleta}
+\end{figure}
 
-\section{Results}
+Similarly we may see the effects of the density on the alignment of birds.
+This also fits the prediction from equation~\eqref{eq:va-rho}\todo{Does the effect of density fit the prediction?}.
+This is shown in figure~\ref{fig:va_over_rho}.
 
-\begin{table}
-\caption{Example table}
+\begin{figure}[!htb]
 	\centering
-\begin{tabular}{llr}
-\toprule
-\multicolumn{2}{c}{Name} \\
-\cmidrule(r){1-2}
-First name & Last Name & Grade \\
-\midrule
-John & Doe & $7.5$ \\
-Richard & Miles & $2$ \\
-\bottomrule
-\end{tabular}
-\end{table}
+	\includegraphics[width=\columnwidth]{va_over_rho}
+	\caption{Dependance of alignment on density}
+  \label{fig:va_over_rho}
+\end{figure}
 
-\blindtext % Dummy text
+\subsection{Cone-like vision}
+\label{subsec:conevision}
 
-\begin{equation}
-\label{eq:emc}
-e = mc^2
-\end{equation}
+The effects of our implementation of an angle based vision are only detectable on both low randomness and low density.
+This is expected as a higher density causes an effective long range interaction, which may span the entire flock\todo{Is long range interaction described?}.
+This negates the effect of an angle based vision as the flock moves in a coherent fashion.
+As for randomness of motion it decreases the overall alignment of the flock as seen in figure~\ref{fig:va_over_eta}.
+In figure~\ref{fig:conevision} we present the overall alignment's dependance of the angle describing this cone-like vision for different densities.
+The randomness is kept at a low value of $\eta=0.1$.
+The results correspond quite well with our expectation of increasing the alignment with larger angle and for an angle of 180 degrees we see, the alignment looks like it did when we considered everything within a circle.
+We also notice the effects of the density of birds.
+As described above we expect a long range interaction between the birds to arise when the density increases.
+This effect is visible in the figure as we see the alignment increase faster, when the density is higher.
 
-\blindtext % Dummy text
+\begin{figure}[!htb]
+\label{fig:conevision}
+  \begin{center}
+    \includegraphics[width=\columnwidth]{va_over_angle}
+  \end{center}
+  \caption{Conevision}
+\end{figure}
 
-%------------------------------------------------
+\todo[inline]{There is something about how the alignment only starts increasing once the angle increases above 25 degrees}
 
@@
 
-\subsection{Subsection One}
+We have compared the collective motion of birds to a thermodynamic phase transition.
+The connection between these is not obvious.
+However we see simlilarities in how increasing the randomness\todo{temperature?} will distrupt alignment and how denser systems will display longer effective interaction range.
 
-A statement requiring citation \cite{Figueredo:2009dg}.
-\blindtext % Dummy text
+The addition of a cone-like vision is, as the name suggests, inspired from birds rather than thermodynamics.
+To our knowledge it doesn't have an equivalent in this field\todo{does it?}, \todo[inline]{however it might tell us something about directional interaction}
 
-\subsection{Subsection Two}
-
-\blindtext % Dummy text
+The values of $v_a$ have been taken as a time average after some transient time after which the system has settled into a state, which doesn't change significantly.
 
@@
 
-\bibitem[Figueredo and Wolf, 2009]{Figueredo:2009dg}
-Figueredo, A.~J. and Wolf, P. S.~A. (2009).
-\newblock Assortative pairing and life history strategy - a cross-cultural
-  study.
-\newblock {\em Human Nature}, 20:317--330.
+  \bibitem{Vicsek}Vicsek
 

### 2017-10-28 tex/article.tex
conclusion

@@
 
+\section{Conclusion}
+
+In this paper we have presetend a model for studying the behaviour of interacting particles.
+The interaction between particles consisted in maintaining the average velocity of nearby neighbours.
+The system was studied when particles shared a common interaction radius and when each particle had a cone of vision.
+During the simulation it has been observed that the system goes through a phase transition where all particles assume the same direction.
+In order to describe the transition we have calculated the average normalized velocity va and investigated how it behaves when we modify the parameters of the system.
+In the thermodynamic limit va can be described using (5) or (6).
+By plotting these equations we have found  the critical exponent $\beta$ to be equal to ....
+
 %----------------------------------------------------------------------------------------

### 2017-10-28 tex/article.tex
comment on figure

@@
 
+\todo{
+TO EDIT
+For the disordered phase $v_a$ is aproximatively 0, while for the ordered phase $v_a$ has the value of 1.
+%rephrase:
+In the following figure we show how $v_a$ varies with the noise $\eta$ and density  $\rho$ for a constant value of density and noise respectively.
+
+As it can be seen from the graph the overall alignment of the particles depends on the noise and for a high number of particles N the system becomes more disordered.
+
+For high values of density the flock reaches a coherent moving phase, while for low values of density the particles move randomly in the lattice.
+
+TO EDIT
+
+}
+
 \begin{figure}[!htb]

### 2017-10-29 tex/article.tex
Calculation of eta_c via fit added
some changes in article.tex

--- 2017-10-28 tex/article.tex
@@
 \end{equation}
-For the disordered phase $v_a$ is aproximatively 0, while for the ordered phase $v_a$ has the value of 1.
-\todo{refrace}
+% Note: here you had a sentence about eta->0 for an unordered and eta->1 for an
+% ordered state, this is already explained in more detail in the results and,
+% i guess, makes more sense there.
 
@@
 \todo[inline]{This needs to be much clearer. It is not obvious how this behaviour is similar or why it's reasonable to assume it would be}
+
+\subsection{Finding $\eta_c$}
+To determine the critical noise parameter $\eta_c$ we used a quadratic fit model
+to to fit the falling curve for $\eta < \eta_c$ and a linear fit for $\eta > 
+\eta_c$, both visible in figure~\ref{fig:va_over_eta}. $\eta_c$ is then set to 
+the intersection of the fit curves. Hereby we determine
+\begin{align}
+\eta_c = 4.56***
+\end{align}
+\todo{put in final number}
 
@@
 
-We further extend the model by implementing a cone-like vision.
-This means, that rather than averaging the velocities over all birds within a certian radius, we only look at a slice of this circle.
-For a bird to be within the vision of another bird, it must be within the interaction radius, $r$, and the angle between the birds velocities must be within $\pm \theta_{cone}$.
-In the limit $\theta_{cone} = 180 \deg$\todo{use radians for paper?} we should see the same behavior of the model as without implementation of this vision.
+We further extend the model by implementing a cone-like vision. This means, that 
+rather than averaging the velocities over all birds within a certian radius, we 
+only look at a slice of this circle. For a bird to be within the vision of 
+another bird, it must be within the interaction radius, $r$, and the angle 
+between the birds velocities must be within $\pm \theta_{\text{cone}}$. The 
+limit $\theta_{\text{cone}} = 2\pi$ equals the case without limiting the
+cone vision and reprocuces the results from \cite{Vicsek}.
 
@@
 
-The alignment, $v_a$, depends on the amount of randomness, $\eta$, in the system and the density, $\rho$, as seen in equations~\eqref{eq:va-eta} and \eqref{eq:va-rho}.
-In Figure\ref{fig:va_over_eta} we see how, the alignment of the birds decreases as the randomness of their motion increases.
-The decrease is to be expected as a higher degree of randomness should disrupt alignment.
-What might be more interesting is the general shape of the curves.
-We may then determine $\beta$ from equation\eqref{eq:va-eta} to be \todo{get value of $\beta$} \todo{What do we use $\beta$ for?}.
-This is also shown in figure~\ref{fig:criticaleta}.
-The results presented here are all computed without the conevision (or with $\theta_{cone} = 180\deg$)\todo{use radians for paper?}.
-The effects of it will be presented in \ref{subsec:results_conevision}.
+The alignment, $v_a$, depends on the amount of randomness $\eta$ in the system 
+and the density $\rho$, as seen in equations~\eqref{eq:va-eta} and 
+\eqref{eq:va-rho}. In figure~\ref{fig:va_over_eta} we see how the alignment of 
+the birds decreases as the randomness of their motion increases. The decrease 
+is to be expected, as a higher degree of randomness should disrupt alignment. 
+This reflects to $v_a$, which approaches $0$ in a totally unordered state and $1$
+in a totally ordered state.
+What might be more interesting is the general shape of the curves. We may then 
+determine $\beta$ from equation~\eqref{eq:va-eta} to be \todo{get value of $\beta$} \todo{What do we use $\beta$ for?}. 
+This is also shown in figure~\ref{fig:criticaleta}. The results presented here 
+are all computed without the conevision (equivalent to $\theta_{\text{cone}} = 2\pi$). 
+Figure~\ref{fig:va_over_eta} shows how $v_a$ varies with the noise $\eta$ and 
+density $\rho$ for a constant value of density and noise respectively.
+As it can be seen from the graph the overall alignment of the particles depends 
+on the noise and for a high number of particles N the system becomes less ordered. 
+For high $\eta$ the flock reaches a coherent moving phase, while for low $\eta$ 
+the particles move randomly in the lattice.
 
@@
   \includegraphics[width=\columnwidth]{va_over_eta}
-  \caption{Dependance of alignment on randomness}
+  \caption{Dependence of alignment on randomness}
   \label{fig:va_over_eta}
@@
 
-We have compared the collective motion of birds to a thermodynamic phase transition.
-The connection between these is not obvious.
-However we see simlilarities in how increasing the randomness\todo{temperature?} will distrupt alignment and how denser systems will display longer effective interaction range.
+We have compared the collective motion of birds to a thermodynamic phase 
+transition. However we see simlilarities in how increasing the randomness\todo{temperature?} will distrupt alignment and how more dense systems will display longer effective interaction range.
 

### 2017-10-29 tex/article.tex
Update images of configurations of rho and eta + write more in depth

--- 2017-10-28 tex/article.tex
@@
 In this paper we present a model for studying the behaviour of a group of particles which have some level of interaction between them.
-The model was inspired from the~\cite{Vicsek} paper\todo{Present paper and author by name.
+The model was inspired from the~\cite{Vicsek} paper\todo[inline]{Present paper and author by name.
 Also it probably shouldn't be in the abstract} and as in~\cite{Vicsek} the particles have a constant absolute velocity and at each time step  assume the average direction of nearby neighbours with some added perturbation, $\eta$.
@@
 
-The particles where distributed randomly in a square lattice of size L.
+One may consider the collective movement of birds to be described by a simple set of rules.
+In this paper we describe the movement of such a flock as a system of self-propelled particles.
+The movement of each bird or particle is governed by the movement of other birds or particles nearby.
+In the following we may use birds and particles interchangably.
+
+In our setup the particles where distributed randomly in a square lattice of size L.
 Each particle had assigned a random direction $\theta$ and a constant interaction radius r.
@@
 \begin{equation}
-\braket{\theta(t)}_r=\arctan\frac{\braket{sin(\theta(t))}_r}{\braket{cos(\theta(t))}_r}
+\braket{\theta(t)}_r=\arctan\frac{\braket{\sin(\theta(t))}_r}{\braket{\cos(\theta(t))}_r}
 \end{equation}
-is the average direction of the velocities of nearby particles wich are inside the influence circle of radius r of the given particle.$\Delta$t represents the noise in the system and takes values with equal probability within the interval $[-\eta/2,\eta/2]$.
-For a constant number of particles there are 3 parameters which can be varied: $\eta$,$\rho$,and v, where v is the distance a particle travels between 2 updates.
+is the average direction of the velocities of nearby particles wich are inside the influence circle of radius r of the given particle.
+$\Delta \theta$ represents the noise in the system and takes values with equal probability within the interval $[-\eta/2,\eta/2]$.
+For a constant number of particles there are 3 parameters which can be varied: $\eta$,$\rho$,and $v$, where $v$ is the distance a particle travels between 2 updates.
+$\eta$ describes the interval in which $\Delta\theta$ is picked.
+$\rho$ is the density of the particles.
+This is effectively a way of controlling the size of the lattice if the number of particles is fixed.
+
 \begin{figure}[!htb]
 	\centering
-	\subfloat{{\includegraphics[width=\columnwidth/2]{test1}}}
-  \subfloat{{\includegraphics[width=\columnwidth/2]{test2}}}
+	\subfloat{{\includegraphics[width=\columnwidth/2]{low-eta-low-rho}}}
+  \subfloat{{\includegraphics[width=\columnwidth/2]{low-eta-high-rho}}}
 	\qquad
-	\subfloat{{\includegraphics[width=\columnwidth/2]{test2}}}
-	\subfloat{{\includegraphics[width=\columnwidth/2]{test2}}}
+	\subfloat{{\includegraphics[width=\columnwidth/2]{high-eta-low-rho}}}
+	\subfloat{{\includegraphics[width=\columnwidth/2]{high-eta-high-rho}}}
 	\caption{test for figures}
@@
 
-Figure~\ref{fig:configs} shows the configuration of birds for different values of rho and eta.
+Figure~\ref{fig:configs} shows the configuration of birds for different values of $\rho$ and $\eta$.  
+If the density is high enough, while the noise has low values, the system goes through a kinetic phase transition where all the particles share the same direction.
+In order to characterize the behaviour of the flock we have determined the average normalized velocity of the system and investigated how it changes when the input parameters are modified:
 
-If the density is high enough, while the noise has low values, the system goes through a kinetic phase transition where all the particles share the same direction.
-In order to study this behaviour we have determined the average normalized velocity of the system and investigated how it changes when certain parameters are modified:
 \begin{equation}
@@
 \end{equation}
+
 For the disordered phase $v_a$ is aproximatively 0, while for the ordered phase $v_a$ has the value of 1.
-\todo{refrace}
+\todo[inline]{refrace}
 
@@
 For large system sizes the data shows scaling which is an indication of a phase transition.
-Therefore it's possible to describe the behaviour of $v_a$ in the thermodynamic limit using the following equations:
-\todo[inline]{This needs to be much clearer. It is not obvious how this behaviour is similar or why it's reasonable to assume it would be}
+Equations~\eqref{eq:va-eta} and~\eqref{eq:va-rho} may be used to describe such a system near the critical value, at which the phase transition occours.
+
+\subsection{Finding $\eta_c$}
+To determine the critical noise parameter $\eta_c$ we used a quadratic fit model
+to to fit the falling curve for $\eta < \eta_c$ and a linear fit for $\eta > 
+\eta_c$, both visible in Fig.~\ref{fig:va_over_eta}. $\eta_c$ is then set to 
+the intersection of the fit curves.
 
@@
   \label{eq:va-rho}
-  v_a \approx[\rho-\rho_c(eta)]^\gamma
+  v_a \approx[\rho-\rho_c(\eta)]^\gamma
 \end{equation}
@@
 For a bird to be within the vision of another bird, it must be within the interaction radius, $r$, and the angle between the birds velocities must be within $\pm \theta_{cone}$.
-In the limit $\theta_{cone} = 180 \deg$\todo{use radians for paper?} we should see the same behavior of the model as without implementation of this vision.
+In the limit $\theta_{cone} = 180 \deg$\todo[inline]{use radians for paper?} we should see the same behavior of the model as without implementation of this vision.
 
@@
 What might be more interesting is the general shape of the curves.
-We may then determine $\beta$ from equation\eqref{eq:va-eta} to be \todo{get value of $\beta$} \todo{What do we use $\beta$ for?}.
+We may then determine $\beta$ from equation\eqref{eq:va-eta} to be \todo[inline]{get value of $\beta$} \todo[inline]{What do we use $\beta$ for?}.
 This is also shown in figure~\ref{fig:criticaleta}.
-The results presented here are all computed without the conevision (or with $\theta_{cone} = 180\deg$)\todo{use radians for paper?}.
+The results presented here are all computed without the conevision (or with $\theta_{cone} = 180\deg$)\todo[inline]{use radians for paper?}.
 The effects of it will be presented in \ref{subsec:results_conevision}.
 
-\todo{
+\todo[inline]{
 TO EDIT
@@
 Similarly we may see the effects of the density on the alignment of birds.
-This also fits the prediction from equation~\eqref{eq:va-rho}\todo{Does the effect of density fit the prediction?}.
+This also fits the prediction from equation~\eqref{eq:va-rho}\todo[inline]{Does the effect of density fit the prediction?}.
 This is shown in figure~\ref{fig:va_over_rho}.
@@
 The effects of our implementation of an angle based vision are only detectable on both low randomness and low density.
-This is expected as a higher density causes an effective long range interaction, which may span the entire flock\todo{Is long range interaction described?}.
+This is expected as a higher density causes an effective long range interaction, which may span the entire flock\todo[inline]{Is long range interaction described?}.
 This negates the effect of an angle based vision as the flock moves in a coherent fashion.
@@
 \begin{figure}[!htb]
-\label{fig:conevision}
   \begin{center}
@@
   \caption{Conevision}
+  \label{fig:conevision}
 \end{figure}
@@
 The connection between these is not obvious.
-However we see simlilarities in how increasing the randomness\todo{temperature?} will distrupt alignment and how denser systems will display longer effective interaction range.
+However we see simlilarities in how increasing the randomness\todo[inline]{temperature?} will distrupt alignment and how denser systems will display longer effective interaction range.
 
 The addition of a cone-like vision is, as the name suggests, inspired from birds rather than thermodynamics.
-To our knowledge it doesn't have an equivalent in this field\todo{does it?}, \todo[inline]{however it might tell us something about directional interaction}
+To our knowledge it doesn't have an equivalent in this field\todo[inline]{does it?}, \todo[inline]{however it might tell us something about directional interaction}
 
@@
 
-  \bibitem{Vicsek}Vicsek
+  \bibitem{Vicsek}Tamás Vicsek, András Czirók, Eshel Ben-Jacob, Inon Cohen and Ofer Shochet\\
+  Novel Type of Phase Transition in a System of Self-Driven Particles\\
+  Physical Review Letters, Volume 75, Number 6, August 1995
 

### 2017-10-29 tex/article.tex

@@
 \usepackage{subfig}
-
 \usepackage{todonotes}
-
-\usepackage{blindtext} % Package to generate dummy text throughout this template
-
 \usepackage[sc]{mathpazo} % Use the Palatino font
@@
 \usepackage{microtype} % Slightly tweak font spacing for aesthetics
-
 \usepackage[english]{babel} % Language hyphenation and typographical rules
-
 \usepackage[hmarginratio=1:1,top=32mm,columnsep=20pt]{geometry} % Document margins
@@
 \usepackage{titling} % Customizing the title section
-
 \usepackage{hyperref} % For hyperlinks in the PDF
-
 \usepackage{amssymb,amsmath,bbold,braket}
@@
 \begin{abstract}
-\noindent %\blindtext % Dummy abstract text - replace \blindtext with your abstract text
-
+\noindent
 In this paper we present a model for studying the behaviour of a group of particles which have some level of interaction between them.
@@
 The average velocity $v_a$ played the role of an order parameter and it scaled with $(\eta_c-\eta)^\beta$, where $\beta$ is a critical exponent.
-
 \end{abstract}
@@
 \begin{document}
-
-% Print the title
 \maketitle
@@
 	\subfloat{{\includegraphics[width=\columnwidth/2]{high-eta-high-rho}}}
-	\caption{test for figures}
-  \label{fig:configs}
+	\caption{Different configurations of $\eta$ and $\rho$\\Top left: low $\eta$ low $\rho$\\Top right: Low $\eta$, high $\rho$\\Bottm left: High $\eta$, low $\rho$\\Bottom right: High $\eta$, high $\rho$}\label{fig:configs}
 \end{figure}
@@
 Figure~\ref{fig:configs} shows the configuration of birds for different values of $\rho$ and $\eta$.  
-If the density is high enough, while the noise has low values, the system goes through a kinetic phase transition where all the particles share the same direction.
-In order to characterize the behaviour of the flock we have determined the average normalized velocity of the system and investigated how it changes when the input parameters are modified:
+For low values of both $\rho$ and $\eta$ the birds tend to form smaller groups in which the birds move in the same direction.
+The groups themselves move randomly.
+When the randomness is high and the density low, the overall motion of the birds is just random.
+In the case of high randomness and high density, the birds appear to move randomly but with an overall trend in directions
+shared among the all the birds.
+If the density is high enough, while the noise has low values, the virds move ordly in one direction.
+This overall trend in motion is similar to the system going through a kinetic phase transition
+where all the particles share the same direction. In order to characterize the behaviour of the flock
+we have determined the average normalized velocity of the system and investigated how it changes when the input parameters are modified:
 
@@
 
-For the disordered phase $v_a$ is aproximatively 0, while for the ordered phase $v_a$ has the value of 1.
-\todo[inline]{refrace}
+For disordered motion $v_a$ is aproximatively 0, while for ordered $v_a$ has the value near 1.
 
@@
 to to fit the falling curve for $\eta < \eta_c$ and a linear fit for $\eta > 
-\eta_c$, both visible in Fig.~\ref{fig:va_over_eta}. $\eta_c$ is then set to 
-the intersection of the fit curves.
+\eta_c$, both visible in figure~\ref{fig:va_over_eta}. $\eta_c$ is then set to 
+the intersection of the fit curves. Hereby we determine
+\begin{align}
+\eta_c = 4.56***
+\end{align}
+\todo[inline]{put in final number}
 
@@
   \label{eq:va-eta}
-  v_a \approx[\eta_c(\rho)-\eta]^\beta 
+  v_a \approx{[\eta_c(\rho)-\eta]}^\beta 
 \end{equation}
@@
   \label{eq:va-rho}
-  v_a \approx[\rho-\rho_c(\eta)]^\gamma
+  v_a \approx{\left[\rho-\rho_c (\eta)\right]}^\gamma
 \end{equation}
 
-We further extend the model by implementing a cone-like vision.
-This means, that rather than averaging the velocities over all birds within a certian radius, we only look at a slice of this circle.
-For a bird to be within the vision of another bird, it must be within the interaction radius, $r$, and the angle between the birds velocities must be within $\pm \theta_{cone}$.
-In the limit $\theta_{cone} = 180 \deg$\todo[inline]{use radians for paper?} we should see the same behavior of the model as without implementation of this vision.
+We further extend the model by implementing a cone-like vision. This means, that 
+rather than averaging the velocities over all birds within a certian radius, we 
+only look at a slice of this circle. For a bird to be within the vision of 
+another bird, it must be within the interaction radius, $r$, and the angle 
+between the birds velocities must be within $\pm \theta_{\text{cone}}$. The 
+limit $\theta_{\text{cone}} = 2\pi$ equals the case without limiting the
+cone vision and reprocuces the results from~\cite{Vicsek}.
 
@@
 
-The alignment, $v_a$, depends on the amount of randomness, $\eta$, in the system and the density, $\rho$, as seen in equations~\eqref{eq:va-eta} and \eqref{eq:va-rho}.
-In Figure\ref{fig:va_over_eta} we see how, the alignment of the birds decreases as the randomness of their motion increases.
-The decrease is to be expected as a higher degree of randomness should disrupt alignment.
-What might be more interesting is the general shape of the curves.
-We may then determine $\beta$ from equation\eqref{eq:va-eta} to be \todo[inline]{get value of $\beta$} \todo[inline]{What do we use $\beta$ for?}.
-This is also shown in figure~\ref{fig:criticaleta}.
-The results presented here are all computed without the conevision (or with $\theta_{cone} = 180\deg$)\todo[inline]{use radians for paper?}.
-The effects of it will be presented in \ref{subsec:results_conevision}.
-
-\todo[inline]{
-TO EDIT
-For the disordered phase $v_a$ is aproximatively 0, while for the ordered phase $v_a$ has the value of 1.
-%rephrase:
-In the following figure we show how $v_a$ varies with the noise $\eta$ and density  $\rho$ for a constant value of density and noise respectively.
-
-As it can be seen from the graph the overall alignment of the particles depends on the noise and for a high number of particles N the system becomes more disordered.
-
-For high values of density the flock reaches a coherent moving phase, while for low values of density the particles move randomly in the lattice.
-
-TO EDIT
-
-}
+The alignment, $v_a$, depends on the amount of randomness $\eta$ in the system 
+and the density $\rho$, as seen in equations~\eqref{eq:va-eta} and~\eqref{eq:va-rho}.
+In figure~\ref{fig:va_over_eta} we see how the alignment of 
+the birds decreases as the randomness of their motion increases. The decrease 
+is to be expected, as a higher degree of randomness should disrupt alignment. 
+This reflects to $v_a$, which approaches $0$ in a totally unordered state and $1$
+in a totally ordered state.
+What might be more interesting is the general shape of the curves. We may then 
+determine $\beta$ from equation~\eqref{eq:va-eta} to be \todo[inline]{get value of $\beta$}
+This is also shown in figure~\ref{fig:criticaleta}. The results presented here 
+are all computed without the conevision (equivalent to $\theta_{\text{cone}} = 2\pi$). 
+Figure~\ref{fig:va_over_eta} shows how $v_a$ varies with the noise $\eta$ and 
+density $\rho$ for a constant value of density and noise respectively.
+As seen in the graph the overall alignment of the particles depends 
+on the noise and for a high number of particles N the system becomes less ordered. 
+For high $\eta$ the flock reaches a coherent moving phase, while for low $\eta$ 
+the particles move randomly in the lattice.
 
@@
   \includegraphics[width=\columnwidth]{va_over_eta}
-  \caption{Dependance of alignment on randomness}
-  \label{fig:va_over_eta}
+  \caption{Dependence of alignment on randomness}\label{fig:va_over_eta}
 \end{figure}
@@
 	\includegraphics[width=\columnwidth]{va_over_etac_minus_eta_over_etac}
-	\caption{Determining $\beta$}
-  \label{fig:criticaleta}
+	\caption{Determining $\beta$}\label{fig:criticaleta}
 \end{figure}
@@
 	\includegraphics[width=\columnwidth]{va_over_rho}
-	\caption{Dependance of alignment on density}
-  \label{fig:va_over_rho}
+	\caption{Dependance of alignment on density}\label{fig:va_over_rho}
 \end{figure}
@@
 The effects of our implementation of an angle based vision are only detectable on both low randomness and low density.
-This is expected as a higher density causes an effective long range interaction, which may span the entire flock\todo[inline]{Is long range interaction described?}.
+This is expected as a higher density causes an effective long range interaction, which may span the entire flock.
 This negates the effect of an angle based vision as the flock moves in a coherent fashion.
 As for randomness of motion it decreases the overall alignment of the flock as seen in figure~\ref{fig:va_over_eta}.
-In figure~\ref{fig:conevision} we present the overall alignment's dependance of the angle describing this cone-like vision for different densities.
-The randomness is kept at a low value of $\eta=0.1$.
-The results correspond quite well with our expectation of increasing the alignment with larger angle and for an angle of 180 degrees we see, the alignment looks like it did when we considered everything within a circle.
-We also notice the effects of the density of birds.
-As described above we expect a long range interaction between the birds to arise when the density increases.
+In figure~\ref{fig:conevision} we present the overall alignment's dependance of the angle describing this cone-like
+vision for different densities. The randomness is kept at a low value of $\eta=0.1$.
+The results correspond quite well with our expectation of increasing the alignment with larger angle.
+For an angle of 180 degrees we see, the alignment looks like it did when we considered every bird within the interaction radius.
+We also notice the effects of the density of birds. As described above we expect a long range interaction
+between the birds to arise when the density increases.
 This effect is visible in the figure as we see the alignment increase faster, when the density is higher.
@@
 \end{center}
-  \caption{Conevision}
-  \label{fig:conevision}
+\caption{Conevision}\label{fig:conevision}
 \end{figure}
-
-\todo[inline]{There is something about how the alignment only starts increasing once the angle increases above 25 degrees}
 
@@
 
-We have compared the collective motion of birds to a thermodynamic phase transition.
-The connection between these is not obvious.
-However we see simlilarities in how increasing the randomness\todo[inline]{temperature?} will distrupt alignment and how denser systems will display longer effective interaction range.
+We have compared the collective motion of birds to a phase transition.
+The connection between these is not obvious. However we do see simlilarities in how increasing the noise in the system
+will distrupt alignment and how denser systems will display longer effective interaction range. Causing the entire
+system to behave coherently.
 
-The addition of a cone-like vision is, as the name suggests, inspired from birds rather than thermodynamics.
-To our knowledge it doesn't have an equivalent in this field\todo[inline]{does it?}, \todo[inline]{however it might tell us something about directional interaction}
+The addition of a cone-like vision is, as the name might suggests, inspired from birds rather than the study of phase transitions.
+The effects of the vision based approach were suttle. They were only detectable for low densities and noise, and for
+sufficiently large angles of vision the system would again display behavior to that without the vision based approach.
 
@@
 In the thermodynamic limit va can be described using (5) or (6).
-By plotting these equations we have found  the critical exponent $\beta$ to be equal to ....
+By plotting these equations we have found  the critical exponent $\beta$ to be equal to\todo[inline]{$\beta$}
 

### 2017-10-29 tex/article.tex
More text -- yay for good commit messages

@@
 In this paper we describe the movement of such a flock as a system of self-propelled particles.
-The movement of each bird or particle is governed by the movement of other birds or particles nearby.
+Our model is an extension of the model presented by Tamás Vicsek and his group in their paper ``Novel Type of Phase Transition in a System of Self-Driven Particles''~\cite{Vicsek}.
+The motion of each bird or particle is governed by the motion of other birds or particles nearby.
 In the following we may use birds and particles interchangably.
 
-In our setup the particles where distributed randomly in a square lattice of size L.
-Each particle had assigned a random direction $\theta$ and a constant interaction radius r.
+In our setup the particles where distributed randomly in a square lattice of size $L$.
+Each particle had assigned a random direction $\theta$ and a constant interaction radius $r$.
 One update consisted in modifying the position of all particles according to the following equation:
@@
 \end{equation}
+
 where $\Delta$t represents the time between 2 updates.
 The velocity of a particle had a constant absolute value and a direction given by:
+
 \begin{equation}
@@
 where
+
 \begin{equation}
@@
 \end{equation}
-is the average direction of the velocities of nearby particles wich are inside the influence circle of radius r of the given particle.
+%
+is the average direction of the velocities of nearby particles wich are inside the radius of influence, $r$, of the given particle.
 $\Delta \theta$ represents the noise in the system and takes values with equal probability within the interval $[-\eta/2,\eta/2]$.
-For a constant number of particles there are 3 parameters which can be varied: $\eta$,$\rho$,and $v$, where $v$ is the distance a particle travels between 2 updates.
-$\eta$ describes the interval in which $\Delta\theta$ is picked.
-$\rho$ is the density of the particles.
+For a constant number of particles there are 3 parameters which can be varied: $\eta$,$\rho$,and $v$,
+where $v$ is the distance a particle travels between 2 updates.
+$\eta$ describes the interval in which $\Delta\theta$ is picked. $\rho$ is the density of the particles.
 This is effectively a way of controlling the size of the lattice if the number of particles is fixed.
+
+We further extend the model by implementing a cone-like vision. This means, that 
+rather than averaging the velocities over all birds within a certian radius, we 
+only look at a slice of this circle. For a bird to be within the vision of 
+another bird, it must be within the interaction radius, $r$, and the angle 
+between the birds velocities must be within $\pm \theta_{\text{cone}}$. The 
+limit $\theta_{\text{cone}} = 2\pi$ equals the case without limiting the
+cone vision and reprocuces the results from~\cite{Vicsek}.
 
@@
 
-\subsection{Finding $\eta_c$}
+\subsection{Determining the critical noise level}
 To determine the critical noise parameter $\eta_c$ we used a quadratic fit model
@@
 \end{equation}
-
-We further extend the model by implementing a cone-like vision. This means, that 
-rather than averaging the velocities over all birds within a certian radius, we 
-only look at a slice of this circle. For a bird to be within the vision of 
-another bird, it must be within the interaction radius, $r$, and the angle 
-between the birds velocities must be within $\pm \theta_{\text{cone}}$. The 
-limit $\theta_{\text{cone}} = 2\pi$ equals the case without limiting the
-cone vision and reprocuces the results from~\cite{Vicsek}.
 

### 2017-10-29 tex/article.tex
Update conclusion

@@
 \noindent
-In this paper we present a model for studying the behaviour of a group of particles which have some level of interaction between them.
-The model was inspired from the~\cite{Vicsek} paper\todo[inline]{Present paper and author by name.
-Also it probably shouldn't be in the abstract} and as in~\cite{Vicsek} the particles have a constant absolute velocity and at each time step  assume the average direction of nearby neighbours with some added perturbation, $\eta$.
-The behaviour was studied by analysing how the average velocity of the flock $v_a$ varied when parameters like noise, density, number of particles where changed.
+% In this paper we present a model for studying the behaviour of a group of particles which have some level of interaction between them.
+The model was inspired from the~\cite{Vicsek} paper the particles have a constant absolute velocity and at each time step  assume the average direction of nearby neighbours with some added perturbation, $\eta$.
+%The behaviour was studied by analysing how the average velocity of the flock $v_a$ varied when parameters like noise, density, number of particles where changed.
 In addition to $[1]$ we have introduced a cone of vision for every particle and studied the behaviour of the flock in the same conditions.
@@
 The average velocity $v_a$ played the role of an order parameter and it scaled with $(\eta_c-\eta)^\beta$, where $\beta$ is a critical exponent.
+The motion of a flock of birds appears complex and difficult to classify due to
+the large number of paticipants each with their own idea of where to go.
+Yet such flocks display clear collective motion. In this paper we describe such a flock
+similar to a system of self-propelled particles interacting with nearby neighbours.
+We extend this model by reducing the interaction of any given bird by only interacting with other birds
+within the bird's vision. Any bird will act as an average of any other birds it can see.
+We show that this simple model of limited interaction may cause the flock to align
+over distances larger than the extend of a single bird's interaction. Including how
+the noise in each bird's direction and density of birds affect the alignment.
+We compare the transition from unordered to ordered motion to a phase transition and
+comment on the effects of a vision based approach to this transition.
 \end{abstract}
@@
 another bird, it must be within the interaction radius, $r$, and the angle 
-between the birds velocities must be within $\pm \theta_{\text{cone}}$. The 
-limit $\theta_{\text{cone}} = 2\pi$ equals the case without limiting the
-cone vision and reprocuces the results from~\cite{Vicsek}.
+between the bird's velocity and direction to the other bird must be within $\pm \theta_{\text{cone}}$. The 
+limit $\theta_{\text{cone}} = \pi$ equals the case without limiting the
+cone vision and reproduces the results from~\cite{Vicsek}.
 
@@
 shared among the all the birds.
-If the density is high enough, while the noise has low values, the virds move ordly in one direction.
+If the density is high enough, while the noise has low values, the birds move orderly in one direction.
 This overall trend in motion is similar to the system going through a kinetic phase transition
@@
 
-\subsection{Cone-like vision}
-\label{subsec:conevision}
+\subsection{Cone-like vision}\label{subsec:conevision}
 
@@
 This effect is visible in the figure as we see the alignment increase faster, when the density is higher.
+Again we see, how the system goes between an unordered state and an ordered state.
+For low densities we don't reach full alignment, but that might be due to the lack of interaction between far-away birds.
+The trend however is similar to the phase transition presented earlier.
 
@@
 sufficiently large angles of vision the system would again display behavior to that without the vision based approach.
+As discussed this behavior is similar to that of a phase transition, however it is only detectable for low denisities.
+This also means, that the system doesn't align completely in the range where it is detectable,
+unlike for the other transitions presented in this paper. We have treated the angle of vision more like a property
+of the system than a variable. This is a naive approach as it assumes that any single bird only ever looks in one direction.
 
@@
 
-In this paper we have presetend a model for studying the behaviour of interacting particles.
+% In this paper we have presetend a model for studying the behaviour of interacting particles.
 The interaction between particles consisted in maintaining the average velocity of nearby neighbours.
@@
 In the thermodynamic limit va can be described using (5) or (6).
-By plotting these equations we have found  the critical exponent $\beta$ to be equal to\todo[inline]{$\beta$}
+% By plotting these equations we have found  the critical exponent $\beta$ to be equal to\todo[inline]{$\beta$}
+
+In this paper we have presented a model for studying the motion of a flock of birds.
+The model contained contained few variables; density of birds, noise in their direction and an angle
+controlling which other birds influence a given bird's motion. Each of these variables gave rise
+to the movement of the flock going from disordered to ordered. For the case of the angle of vision
+the transition was only detectable for low densities and low noise as higher densities made more
+birds be within sight and high noise reduced alignment enough for the effect of the vision to be hard to detect.
 

### 2017-10-29 tex/article.tex
Sexyer section titles

@@
 
-\section{Introduction}
+\section{Collective motion of birds}
 
@@
 
-\section{Results}
+% \section{Results}
+\section{From disorder to order}
 
@@
 This is also shown in figure~\ref{fig:criticaleta}. The results presented here 
-are all computed without the conevision (equivalent to $\theta_{\text{cone}} = 2\pi$). 
+are all computed without the conevision (equivalent to $\theta_{\text{cone}} = \pi$). 
 Figure~\ref{fig:va_over_eta} shows how $v_a$ varies with the noise $\eta$ and 
@@
 
-Similarly we may see the effects of the density on the alignment of birds.
-This also fits the prediction from equation~\eqref{eq:va-rho}\todo[inline]{Does the effect of density fit the prediction?}.
-This is shown in figure~\ref{fig:va_over_rho}.
+Similarly we may see the effects of the density on the alignment of birds. This also fits the prediction from equation~\eqref{eq:va-rho}. This is shown in figure~\ref{fig:va_over_rho}.
 
@@
 The results correspond quite well with our expectation of increasing the alignment with larger angle.
-For an angle of 180 degrees we see, the alignment looks like it did when we considered every bird within the interaction radius.
+For an angle of $\pi$ we see, the alignment looks like it did when we considered every bird within the interaction radius.
 We also notice the effects of the density of birds. As described above we expect a long range interaction

### 2017-10-29 src/birds.py
Use correct method of cone vision
This changes the way vision is implemented such that birds actually move
if nothing is within range. This also means our conclusion changes and
is more consistent with previous results

@@ -34,8 +34,7 @@ class Flock:
         if self.args["angle"] == 0:
             self.angle_view = False
         else:
-            # half of viewing angle + deg->rad
-            self.angle_view = self.args["angle"]/360*np.pi
+            self.angle_view = self.args["angle"]/360*np.pi*2
 
 
     def get_va(self):
@@ -52,8 +51,8 @@ class Flock:
 
         # check if viewing-angle (theta_velocity) +- angle_view/2 matches distance-vector to neighbors (theta(pos1-pos2))
         if self.angle_view:
-            #mask *= np.absolute(np.arctan2(self.dy.T, self.dx.T) - np.arctan2(self.velocity[:,1],self.velocity[:,0])) < self.angle_view
-            mask *= np.divide( self.dx.T * self.velocity[:,0] + self.dy.T * self.velocity[:,1], self.distance, np.ones_like(self.distance), where=self.distance!=0) > np.cos(self.angle_view)
+            # mask *= np.absolute(np.arctan2(self.dy.T, self.dx.T) - np.arctan2(self.velocity[:,1],self.velocity[:,0])) < self.angle_view
+            mask *= np.divide( self.dx.T * self.velocity[:,0] + self.dy.T * self.velocity[:,1], self.distance*self.args["v"], np.ones_like(self.distance), where=self.distance!=0) > np.cos(self.angle_view)
 
 
         mask_count = np.maximum(mask.sum(axis=1), 1).reshape(self.args["n"],1)

### 2017-10-30 src/birds.py
Finally found (and fixed) the error in random_turn()

@@ -12,6 +12,7 @@ import time
 import argparse
 
 
+
 class Flock:
     def __init__(self, **kwargs):
 
@@ -37,6 +38,8 @@ class Flock:
             # half of viewing angle + deg->rad
             self.angle_view = self.args["angle"]/360*np.pi
 
+        print('init: '+str(np.mean(self.velocity[:,0]**2+self.velocity[:,1]**2)))
+
 
     def get_va(self):
         n = self.args["n"]
@@ -59,6 +62,7 @@ class Flock:
         mask_count = np.maximum(mask.sum(axis=1), 1).reshape(self.args["n"],1)
 
         self.calc_velocity(mask,mask_count)
+        print('after calc_velocity: '+str(np.mean(self.velocity[:,0]**2+self.velocity[:,1]**2)))
 
         if self.args["eta"]:
             self.random_turn()
@@ -99,15 +103,9 @@ class Flock:
         angles = np.random.uniform(-self.args["eta"]/2,self.args["eta"]/2,self.args["n"])
 
         # Option 1 using addition theorem
-        c = np.cos(angles)
-        s = np.sin(angles)
-        self.velocity[:,0] = self.velocity[:,0]*c - self.velocity[:,1]*s
-        self.velocity[:,1] = self.velocity[:,1]*c + self.velocity[:,0]*s
-
-        # Option 2 using tan/arctan with same result
-        #av = np.arctan2(self.velocity[:,1],self.velocity[:,0])
-        #av += angles
-        #self.velocity = np.array([np.cos(av),np.sin(av)]).reshape(self.args["n"],2)
+        c,s = np.cos(angles), np.sin(angles)
+        # update in parrallel to avoid using updated x to calculate y
+        self.velocity[:,0], self.velocity[:,1] = self.velocity[:,0]*c - self.velocity[:,1]*s, self.velocity[:,1]*c + self.velocity[:,0]*s
 
         return
 

### 2017-10-30 tex/article.tex
Updated figures

@@
 \usepackage{booktabs} % Horizontal rules in tables
-
 \usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
@@
 
-\subsection{Cone-like vision}\label{subsec:conevision}
+\subsection*{Cone-like vision}\label{subsec:conevision}
 
-The effects of our implementation of an angle based vision are only detectable on both low randomness and low density.
-This is expected as a higher density causes an effective long range interaction, which may span the entire flock.
-This negates the effect of an angle based vision as the flock moves in a coherent fashion.
-As for randomness of motion it decreases the overall alignment of the flock as seen in figure~\ref{fig:va_over_eta}.
-In figure~\ref{fig:conevision} we present the overall alignment's dependance of the angle describing this cone-like
-vision for different densities. The randomness is kept at a low value of $\eta=0.1$.
-The results correspond quite well with our expectation of increasing the alignment with larger angle.
-For an angle of $\pi$ we see, the alignment looks like it did when we considered every bird within the interaction radius.
-We also notice the effects of the density of birds. As described above we expect a long range interaction
-between the birds to arise when the density increases.
-This effect is visible in the figure as we see the alignment increase faster, when the density is higher.
-Again we see, how the system goes between an unordered state and an ordered state.
+\todo[inline]{The results in this section were based on code producing wrong results, thus it must be rewritten}
+
+% The effects of our implementation of an angle based vision are only detectable on both low randomness and low density.
+% This is expected as a higher density causes an effective long range interaction, which may span the entire flock.
+% This negates the effect of an angle based vision as the flock moves in a coherent fashion.
+% As for randomness of motion it decreases the overall alignment of the flock as seen in figure~\ref{fig:va_over_eta}.
+% In figure~\ref{fig:conevision} we present the overall alignment's dependance of the angle describing this cone-like
+% vision for different densities. The randomness is kept at a low value of $\eta=0.1$.
+% The results correspond quite well with our expectation of increasing the alignment with larger angle.
+% For an angle of $\pi$ we see, the alignment looks like it did when we considered every bird within the interaction radius.
+% We also notice the effects of the density of birds. As described above we expect a long range interaction
+% between the birds to arise when the density increases.
+% This effect is visible in the figure as we see the alignment increase faster, when the density is higher.
+% Again we see, how the system goes between an unordered state and an ordered state.
 For low densities we don't reach full alignment, but that might be due to the lack of interaction between far-away birds.
 The trend however is similar to the phase transition presented earlier.
+
+The cone-like vision has no or little effect on the final alignment of the birds, only the time it takes to reach this level of alignment.
+What we do see however is the shape of the formed groups. In stead of forming dense groups, the birds now form lines or open
+triangles whose shapes are defined by the angle of vision. An example of such a configuration is seen in Figure~\ref{fig:angle-birds}.
+In Figure~\ref{fig:conevision} we see how the effect of the cone-like vision has little effect on the final alignment.
+There appears to be a slight upward trend for the density $\rho=0.1$.
+This may be attributed to the time taken to reach alignment as each data point has been taken after the same amount of time.
+It may not have been long enough for the smaller angles.
+For the cases $\rho=1,0.01$ They both reach the alignment shown in Figure~\ref{fig:va_over_rho}.
+The runtime before measuring $v_a$ has for Figure~\ref{fig:conevision} been twice as long as for the other figures.
 
@@
 \caption{Conevision}\label{fig:conevision}
+\end{figure}
+
+\begin{figure}[!htb]
+\begin{center}
+\includegraphics[width=\columnwidth]{angles}
+\end{center}
+\caption{Angles  ..... }\label{fig:angle-birds}
 \end{figure}
@@
 The addition of a cone-like vision is, as the name might suggests, inspired from birds rather than the study of phase transitions.
-The effects of the vision based approach were suttle. They were only detectable for low densities and noise, and for
-sufficiently large angles of vision the system would again display behavior to that without the vision based approach.
-As discussed this behavior is similar to that of a phase transition, however it is only detectable for low denisities.
-This also means, that the system doesn't align completely in the range where it is detectable,
-unlike for the other transitions presented in this paper. We have treated the angle of vision more like a property
+\todo[inline]{The previous discussion of cone-like vision was wrong, so rewrite it}
+%The effects of the vision based approach were suttle. They were only detectable for low densities and noise, and for
+%sufficiently large angles of vision the system would again display behavior to that without the vision based approach.
+%As discussed this behavior is similar to that of a phase transition, however it is only detectable for low denisities.
+%This also means, that the system doesn't align completely in the range where it is detectable,
+%unlike for the other transitions presented in this paper.
+We have treated the angle of vision more like a property
 of the system than a variable. This is a naive approach as it assumes that any single bird only ever looks in one direction.

### 2017-10-30 src/birds.py
removed unneccessary output

@@ -37,7 +37,6 @@ class Flock:
         else:
             self.angle_view = self.args["angle"]/360*np.pi*2
 
-        print('init: '+str(np.mean(self.velocity[:,0]**2+self.velocity[:,1]**2)))
 
 
     def get_va(self):
@@ -61,7 +60,6 @@ class Flock:
         mask_count = np.maximum(mask.sum(axis=1), 1).reshape(self.args["n"],1)
 
         self.calc_velocity(mask,mask_count)
-        print('after calc_velocity: '+str(np.mean(self.velocity[:,0]**2+self.velocity[:,1]**2)))
 
         if self.args["eta"]:
             self.random_turn()

### 2017-10-31 tex/article.tex
Update discussion about anglevision and update figures

--- 2017-10-29 tex/article.tex
@@
 We compare the transition from unordered to ordered motion to a phase transition and
-comment on the effects of a vision based approach to this transition.
+comment on how a vision based approach cause triangular groupings similar to those of migratory birds.
 \end{abstract}
@@
 The groups themselves move randomly.
-When the randomness is high and the density low, the overall motion of the birds is just random.
-In the case of high randomness and high density, the birds appear to move randomly but with an overall trend in directions
+When the noise is high and the density low, the overall motion of the birds is just random.
+In the case of high noise and high density, the birds appear to move randomly but with an overall trend in directions
 shared among the all the birds.
@@
 
-For disordered motion $v_a$ is aproximatively 0, while for ordered $v_a$ has the value near 1.
+For disordered motion $v_a$ is aproximatively 0, whereas for ordered motion $v_a$ takes on a value near 1.
+In our calculations the values of $v_a$ have been taken as a time average after some transient time after which the system has settled into a state, which doesn't change significantly.
 
@@
 
-\subsection{Determining the critical noise level}
+\subsection*{Determining the critical noise level}
 To determine the critical noise parameter $\eta_c$ we used a quadratic fit model
@@
 
-The alignment, $v_a$, depends on the amount of randomness $\eta$ in the system 
+The alignment, $v_a$, depends on the amount of noise $\eta$ in the system 
 and the density $\rho$, as seen in equations~\eqref{eq:va-eta} and~\eqref{eq:va-rho}.
@@
 the birds decreases as the randomness of their motion increases. The decrease 
-is to be expected, as a higher degree of randomness should disrupt alignment. 
+is to be expected, as a higher degree of noise should disrupt alignment. 
 This reflects to $v_a$, which approaches $0$ in a totally unordered state and $1$
 in a totally ordered state.
-What might be more interesting is the general shape of the curves. We may then 
+What might be more interesting is the general shape of the curves as they as mentioned are similar to
+that of a phase transition. We may then 
 determine $\beta$ from equation~\eqref{eq:va-eta} to be \todo[inline]{get value of $\beta$}
@@
 density $\rho$ for a constant value of density and noise respectively.
-As seen in the graph the overall alignment of the particles depends 
+As seen in Figure~\ref{fig:va_over_eta} the overall alignment of the particles depends 
 on the noise and for a high number of particles N the system becomes less ordered. 
-For high $\eta$ the flock reaches a coherent moving phase, while for low $\eta$ 
+For low $\eta$ the flock reaches a coherent moving phase, while for high $\eta$ 
 the particles move randomly in the lattice.
@@
   \includegraphics[width=\columnwidth]{va_over_eta}
-  \caption{Dependence of alignment on randomness}\label{fig:va_over_eta}
+  \caption{Dependance of alignment on randomness}\label{fig:va_over_eta}
 \end{figure}
@@
 
-\subsection{Cone-like vision}\label{subsec:conevision}
+\subsection*{Cone-like vision}\label{subsec:conevision}
 
-The effects of our implementation of an angle based vision are only detectable on both low randomness and low density.
-This is expected as a higher density causes an effective long range interaction, which may span the entire flock.
-This negates the effect of an angle based vision as the flock moves in a coherent fashion.
-As for randomness of motion it decreases the overall alignment of the flock as seen in figure~\ref{fig:va_over_eta}.
-In figure~\ref{fig:conevision} we present the overall alignment's dependance of the angle describing this cone-like
-vision for different densities. The randomness is kept at a low value of $\eta=0.1$.
-The results correspond quite well with our expectation of increasing the alignment with larger angle.
-For an angle of $\pi$ we see, the alignment looks like it did when we considered every bird within the interaction radius.
-We also notice the effects of the density of birds. As described above we expect a long range interaction
-between the birds to arise when the density increases.
-This effect is visible in the figure as we see the alignment increase faster, when the density is higher.
-Again we see, how the system goes between an unordered state and an ordered state.
-For low densities we don't reach full alignment, but that might be due to the lack of interaction between far-away birds.
-The trend however is similar to the phase transition presented earlier.
+The cone-like vision has little effect on the final alignment of the birds.
+The effect only becomes apparent near the critical value of $\rho=0.1$ after which
+the alignment increases dramatically as shown in Figure~\ref{fig:va_over_rho}.
+In Figure~\ref{fig:conevision} we see how only the configuration with $\rho$ near the
+transition between the unordered and ordered states is affected by the implementation of the vision.
+There is as expected a slight upward trend in alignment as the angle of the vision is increased.
+A much more interesting result is the shape of the formed groups. In stead of forming
+dense groups, the birds now form lines or open triangles whose shapes are defined
+by the angle of vision. An example of such a configuration is seen in Figure~\ref{fig:angle-birds}.
 
@@
 
+\begin{figure}[!htb]
+\begin{center}
+\includegraphics[width=\columnwidth]{angles}
+\end{center}
+\caption{Birds form lines or triangular groups when a cone-like vision is implemented and the density is low}\label{fig:angle-birds}
+\end{figure}
+
 \section{Discussion}
 
-We have compared the collective motion of birds to a phase transition.
-The connection between these is not obvious. However we do see simlilarities in how increasing the noise in the system
-will distrupt alignment and how denser systems will display longer effective interaction range. Causing the entire
-system to behave coherently.
-
-The addition of a cone-like vision is, as the name might suggests, inspired from birds rather than the study of phase transitions.
-The effects of the vision based approach were suttle. They were only detectable for low densities and noise, and for
-sufficiently large angles of vision the system would again display behavior to that without the vision based approach.
-As discussed this behavior is similar to that of a phase transition, however it is only detectable for low denisities.
-This also means, that the system doesn't align completely in the range where it is detectable,
-unlike for the other transitions presented in this paper. We have treated the angle of vision more like a property
-of the system than a variable. This is a naive approach as it assumes that any single bird only ever looks in one direction.
-
-The values of $v_a$ have been taken as a time average after some transient time after which the system has settled into a state, which doesn't change significantly.
+The shape of the formed groups when implementing the cone-like vision was a surprising result.
+The triangular shape is commonly seen in migratory birds but is usually ascribed to other factors.
+Our simpel model of simply letting the birds do as other birds within their sight reproduces this
+effect. It is easily explained by considering two birds. One approaches the other from the side.
+The first bird will see the other and follow it, whereas the second bird will see nothing and just
+continue. In this way the birds form a line. If birds approach from the other side, they will line
+up in a similar fashion causing a combined triangular shape. Once a traingle has formed it is much
+more likely for a new approaching bird to align with one of the sides of the trangle rather than
+joining the group somewhere else. In this way the triangles keep growing.
+That the effect on alignment is only detectable in a limited range also makes sense, because for
+low densities, it will be unlikely for birds to come close enough to each other to form groups.
+For higher densities there will more often be a bird within any other bird's vision. This causes
+larger, coherent groups to form.
 
 \section{Conclusion}
-
-% In this paper we have presetend a model for studying the behaviour of interacting particles.
-The interaction between particles consisted in maintaining the average velocity of nearby neighbours.
-The system was studied when particles shared a common interaction radius and when each particle had a cone of vision.
-During the simulation it has been observed that the system goes through a phase transition where all particles assume the same direction.
-In order to describe the transition we have calculated the average normalized velocity va and investigated how it behaves when we modify the parameters of the system.
-In the thermodynamic limit va can be described using (5) or (6).
-% By plotting these equations we have found  the critical exponent $\beta$ to be equal to\todo[inline]{$\beta$}
 
@@
 controlling which other birds influence a given bird's motion. Each of these variables gave rise
-to the movement of the flock going from disordered to ordered. For the case of the angle of vision
-the transition was only detectable for low densities and low noise as higher densities made more
-birds be within sight and high noise reduced alignment enough for the effect of the vision to be hard to detect.
+to the movement of the flock going between disordered and ordered. For the case of the angle based
+vision the effects on alignment was only detectable near the transition between the unordered
+and ordered state for the density of birds.
+However the vision based approach gave rise to different shapes of the groups formed when the density
+was sufficiently low. When the vision approach was not used, the groups were dense and clumped
+together. When the vision was implemented, the birds formed lines or triangular groups.
 

### 2017-11-01 tex/article.tex
Minor corrections
Comments on approx. of va

@@
 
-The behaviour of $v_a$ is found to be similar to that of the order parameter of some equilibrium systems close to their critical point.
-For large system sizes the data shows scaling which is an indication of a phase transition.
+The behaviour of $v_a$ is found to be similar to that of the order parameter of some equilibrium systems close to their critical point(like for example the magnetization in the 2D Ising model) if the density is high enough (Fig.2).
+If the density is too low the system doesn't reach the disordered state where $v_a\approx 0$ or in other words it doesn't go through a phase transition.In our case the noise and density played the role of a temperature-like variable.
 Equations~\eqref{eq:va-eta} and~\eqref{eq:va-rho} may be used to describe such a system near the critical value, at which the phase transition occours.
@@
 \end{center}
-\caption{Conevision}\label{fig:conevision}
+\caption{The effect of the cone vision is only visible for adequately small densities}\label{fig:conevision}
 \end{figure}

### 2017-11-01 tex/article.tex
Updated figures and included eta_c and beta

@@
 \noindent
-% In this paper we present a model for studying the behaviour of a group of particles which have some level of interaction between them.
-The model was inspired from the~\cite{Vicsek} paper the particles have a constant absolute velocity and at each time step  assume the average direction of nearby neighbours with some added perturbation, $\eta$.
-%The behaviour was studied by analysing how the average velocity of the flock $v_a$ varied when parameters like noise, density, number of particles where changed.
-In addition to $[1]$ we have introduced a cone of vision for every particle and studied the behaviour of the flock in the same conditions.
-From the simulation results it has been observed that the flock goes through a phase transition where all the particles assume the same direction.
-The average velocity $v_a$ played the role of an order parameter and it scaled with $(\eta_c-\eta)^\beta$, where $\beta$ is a critical exponent.
 The motion of a flock of birds appears complex and difficult to classify due to
@@
 Yet such flocks display clear collective motion. In this paper we describe such a flock
-similar to a system of self-propelled particles interacting with nearby neighbours.
+similar to a system of self-driven particles interacting with nearby neighbours.
 We extend this model by reducing the interaction of any given bird by only interacting with other birds
@@
 One may consider the collective movement of birds to be described by a simple set of rules.
-In this paper we describe the movement of such a flock as a system of self-propelled particles.
+In this paper we describe the movement of such a flock as a system of self-driven particles.
 Our model is an extension of the model presented by Tamás Vicsek and his group in their paper ``Novel Type of Phase Transition in a System of Self-Driven Particles''~\cite{Vicsek}.
 The motion of each bird or particle is governed by the motion of other birds or particles nearby.
-In the following we may use birds and particles interchangably.
 
-In our setup the particles where distributed randomly in a square lattice of size $L$.
-Each particle had assigned a random direction $\theta$ and a constant interaction radius $r$.
-One update consisted in modifying the position of all particles according to the following equation:
+In our setup the birds were distributed randomly in a square lattice of size $L$.
+Each bird had assigned a random direction $\theta$ and a constant interaction radius $r$.
+One update consisted of modifying the position of all birds according to the following equation:
 
@@
 where $\Delta$t represents the time between 2 updates.
-The velocity of a particle had a constant absolute value and a direction given by:
+The velocity of a bird had a constant absolute value and a direction given by:
 
@@
 %
-is the average direction of the velocities of nearby particles wich are inside the radius of influence, $r$, of the given particle.
+is the average direction of the velocities of nearby birds wich are inside the radius of influence, $r$, of the given bird.
 $\Delta \theta$ represents the noise in the system and takes values with equal probability within the interval $[-\eta/2,\eta/2]$.
-For a constant number of particles there are 3 parameters which can be varied: $\eta$,$\rho$,and $v$,
-where $v$ is the distance a particle travels between 2 updates.
-$\eta$ describes the interval in which $\Delta\theta$ is picked. $\rho$ is the density of the particles.
-This is effectively a way of controlling the size of the lattice if the number of particles is fixed.
+For a constant number of birds there are 3 parameters which can be varied: $\eta$,$\rho$,and $v$,
+where $v$ is the distance a bird travels between 2 updates. This taken as a fixed value of 0.03 as recommended by~\cite{Vicsek}.
+$\eta$ describes the interval in which $\Delta\theta$ is picked. $\rho$ is the density of the birds.
+This is effectively a way of controlling the size of the lattice if the number of birds is fixed.
 
@@
 
-Figure~\ref{fig:configs} shows the configuration of birds for different values of $\rho$ and $\eta$.  
+Figure~\ref{fig:configs} shows the configuration of birds for different values of $\rho$ and $\eta$. $\theta_{cone}$ is kept at $\pi$.
 For low values of both $\rho$ and $\eta$ the birds tend to form smaller groups in which the birds move in the same direction.
@@
 
-\subsection*{Determining the critical noise level}
 To determine the critical noise parameter $\eta_c$ we used a quadratic fit model
@@
 \eta_c$, both visible in figure~\ref{fig:va_over_eta}. $\eta_c$ is then set to 
-the intersection of the fit curves. Hereby we determine
-\begin{align}
-\eta_c = 4.56***
-\end{align}
-\todo[inline]{put in final number}
+the intersection of the fit curves. Hereby we determine $\eta_c = 4.25$
 
@@
 that of a phase transition. We may then 
-determine $\beta$ from equation~\eqref{eq:va-eta} to be \todo[inline]{get value of $\beta$}
-This is also shown in figure~\ref{fig:criticaleta}. The results presented here 
+determine $\beta$ from equation~\eqref{eq:va-eta} to be 0.57 for $N=400$. This is also shown in figure~\ref{fig:criticaleta}. The results presented here 
 are all computed without the conevision (equivalent to $\theta_{\text{cone}} = \pi$). 
@@
 density $\rho$ for a constant value of density and noise respectively.
-As seen in Figure~\ref{fig:va_over_eta} the overall alignment of the particles depends 
-on the noise and for a high number of particles N the system becomes less ordered. 
+As seen in Figure~\ref{fig:va_over_eta} the overall alignment of the birds depends 
+on the noise and for a high number of birds N the system becomes less ordered. 
 For low $\eta$ the flock reaches a coherent moving phase, while for high $\eta$ 
-the particles move randomly in the lattice.
+the birds move randomly in the lattice.
 

### 2017-11-02 tex/article.tex
Minor clarifications
so far finished article

@@
 
-\usepackage{subfig}
+\usepackage{subcaption}
 \usepackage{todonotes}
@@
 	\centering
-	\subfloat{{\includegraphics[width=\columnwidth/2]{low-eta-low-rho}}}
-  \subfloat{{\includegraphics[width=\columnwidth/2]{low-eta-high-rho}}}
-	\qquad
-	\subfloat{{\includegraphics[width=\columnwidth/2]{high-eta-low-rho}}}
-	\subfloat{{\includegraphics[width=\columnwidth/2]{high-eta-high-rho}}}
-	\caption{Different configurations of $\eta$ and $\rho$\\Top left: low $\eta$ low $\rho$\\Top right: Low $\eta$, high $\rho$\\Bottm left: High $\eta$, low $\rho$\\Bottom right: High $\eta$, high $\rho$}\label{fig:configs}
+        \begin{subfigure}[b]{0.45\columnwidth}
+	    \includegraphics[width=\columnwidth]{low-eta-low-rho}
+            \caption{Low $\eta$, low $\rho$}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.45\columnwidth}
+            \includegraphics[width=\columnwidth]{low-eta-high-rho}
+            \caption{Low $\eta$, high $\rho$}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.45\columnwidth}
+	    \includegraphics[width=\columnwidth]{high-eta-low-rho}
+            \caption{High $\eta$, low $\rho$}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.45\columnwidth}
+	    \includegraphics[width=\columnwidth]{high-eta-high-rho}
+            \caption{High $\eta$, high $\rho$}
+        \end{subfigure}
+	\caption{Different configurations of $\eta$ and $\rho$}\label{fig:configs}
 \end{figure}
@@
 In the case of high noise and high density, the birds appear to move randomly but with an overall trend in directions
-shared among the all the birds.
+shared among all the birds.
 If the density is high enough, while the noise has low values, the birds move orderly in one direction.
@@
 \eta_c$, both visible in figure~\ref{fig:va_over_eta}. $\eta_c$ is then set to 
-the intersection of the fit curves. Hereby we determine $\eta_c = 4.25$
+the intersection of the fit curves. Hereby we determine $\eta_c = 4.25$ for $N=400$.
 
@@
   \includegraphics[width=\columnwidth]{va_over_eta}
-  \caption{Dependance of alignment on randomness}\label{fig:va_over_eta}
+  \caption{Dependance of alignment on randomness for $\rho = 4$}\label{fig:va_over_eta}
 \end{figure}
@@
 transition between the unordered and ordered states is affected by the implementation of the vision.
-There is as expected a slight upward trend in alignment as the angle of the vision is increased.
+There is, as expected, a slight upward trend in alignment as the angle of the vision is increased.
 A much more interesting result is the shape of the formed groups. In stead of forming
@@
 The triangular shape is commonly seen in migratory birds but is usually ascribed to other factors.
-Our simpel model of simply letting the birds do as other birds within their sight reproduces this
+Our simple model of simply letting the birds do as other birds within their sight reproduces this
 effect. It is easily explained by considering two birds. One approaches the other from the side.
-The first bird will see the other and follow it, whereas the second bird will see nothing and just
-continue. In this way the birds form a line. If birds approach from the other side, they will line
-up in a similar fashion causing a combined triangular shape. Once a traingle has formed it is much
+The foremost bird will see nothing and just continue whereas the approaching bird will see the
+other and follow it.
+In this way the birds form a line. If birds approach from the other side, they will line
+up in a similar fashion causing a combined triangular shape. Once a triangle has formed it is much
 more likely for a new approaching bird to align with one of the sides of the trangle rather than
@@
 In this paper we have presented a model for studying the motion of a flock of birds.
-The model contained contained few variables; density of birds, noise in their direction and an angle
+The model contained few variables: density of birds, noise in their direction and an angle
 controlling which other birds influence a given bird's motion. Each of these variables gave rise

### 2017-11-02 src/birds.py
laserbirds

@@ -35,7 +35,7 @@ class Flock:
         if self.args["angle"] == 0:
             self.angle_view = False
         else:
-            self.angle_view = self.args["angle"]/360*np.pi*2
+            self.angle_view = self.args["angle"]/180*np.pi
 
 
 
@@ -112,7 +112,7 @@ class MarkerCollection:
     Marker collection
     """
 
-    def __init__(self, n=100):
+    def __init__(self, n=100, angle=0, radius=0):
         v = np.array([(-0.25, -0.25), (+0.0, +0.5), (+0.25, -0.25), (0, 0)])
         c = np.array([Path.MOVETO, Path.LINETO, Path.LINETO, Path.CLOSEPOLY])
         self._base_vertices = np.tile(v.reshape(-1), n).reshape(n, len(v), 2)
@@ -121,28 +121,48 @@ class MarkerCollection:
 
         self._scale = np.ones(n)
         self._translate = np.zeros((n, 2))
-        self._rotate = np.zeros(n)
+        self._rotate = np.zeros((n,2))
 
         self._path = Path(vertices=self._vertices.reshape(n*len(v), 2),
                           codes=self._codes)
-        self._collection = PathCollection([self._path], linewidth=0.5,
-                                          facecolor="k", edgecolor="w")
+
+        # viewing cone
+        cos_ang = np.cos(angle/2)
+        sin_ang = np.sin(angle/2)
+        bl = np.tan(np.pi/8) * 4/3
+        v = np.array([(+0.0, +0.0), (-sin_ang*radius, cos_ang*radius), (-sin_ang*radius + cos_ang*bl, cos_ang*radius + sin_ang*bl), (sin_ang*radius, cos_ang*radius), (0,0)])
+        c = np.array([Path.MOVETO, Path.LINETO, Path.CURVE3, Path.CURVE3, Path.CLOSEPOLY]) 
+        self._base_vertices_cone = np.tile(v.reshape(-1),n).reshape(n, len(v), 2)
+        self._vertices_cone = np.tile(v.reshape(-1),n).reshape(n,len(v), 2)
+        self._codes_cone = np.tile(c.reshape(-1), n)
+
+        self._path_cone = Path(vertices=self._vertices_cone.reshape(n*len(v), 2), codes = self._codes_cone)
+
+        
+
+        self._collection = PathCollection([self._path,self._path_cone], linewidths=[0.5, 0.3],
+                                          facecolors=["k","b"], edgecolors=["w","b"])
 
[…]

### 2017-11-02 src/birds.py
display cone

@@ -27,7 +27,7 @@ class Flock:
         # test boid configuration
         if n<=3:
             self.position = np.array([[self.args["width"]/2+15,self.args["height"]/2],[self.args["width"]/2-15,self.args["height"]/2], [self.args["width"]/2,self.args["height"]/2+15]],dtype=np.float32)
-            self.velocity = np.array([[self.args["v"],0],[-self.args["v"],0],[self.args["v"],0]],dtype=np.float32)
+            self.velocity = np.array([[self.args["v"],0],[self.args["v"],0],[self.args["v"],0]],dtype=np.float32)
             self.position = self.position[0:n,:]
             self.velocity = self.velocity[0:n,:]
 
@@ -126,27 +126,40 @@ class MarkerCollection:
         self._path = Path(vertices=self._vertices.reshape(n*len(v), 2),
                           codes=self._codes)
 
-        # viewing cone
-        cos_ang = np.cos(angle/2)
-        sin_ang = np.sin(angle/2)
-        bl = np.tan(np.pi/8) * 4/3
-        v = np.array([(+0.0, +0.0), (-sin_ang*radius, cos_ang*radius), (-sin_ang*radius + cos_ang*bl, cos_ang*radius + sin_ang*bl), (sin_ang*radius, cos_ang*radius), (0,0)])
-        c = np.array([Path.MOVETO, Path.LINETO, Path.CURVE3, Path.CURVE3, Path.CLOSEPOLY]) 
-        self._base_vertices_cone = np.tile(v.reshape(-1),n).reshape(n, len(v), 2)
-        self._vertices_cone = np.tile(v.reshape(-1),n).reshape(n,len(v), 2)
-        self._codes_cone = np.tile(c.reshape(-1), n)
 
-        self._path_cone = Path(vertices=self._vertices_cone.reshape(n*len(v), 2), codes = self._codes_cone)
+        self.cone = True if angle else False
 
-        
+        if self.cone:
 
-        self._collection = PathCollection([self._path,self._path_cone], linewidths=[0.5, 0.3],
-                                          facecolors=["k","b"], edgecolors=["w","b"])
+            # viewing cone
+            cos_ang = np.cos(angle/2)
+            sin_ang = np.sin(angle/2)
+            bl = np.tan(np.pi/8) * 4/3 * radius
+            v_cone = np.array([(+0.0, +0.0), 
+            (-sin_ang*radius, -cos_ang*radius), 
[…]

### 2017-11-02 src/birds.py
improved cones

@@ -35,7 +35,7 @@ class Flock:
         if self.args["angle"] == 0:
             self.angle_view = False
         else:
-            self.angle_view = self.args["angle"]/180*np.pi
+            self.angle_view = self.args["angle"]/2
 
 
 
@@ -134,12 +134,12 @@ class MarkerCollection:
             # viewing cone
             cos_ang = np.cos(angle/2)
             sin_ang = np.sin(angle/2)
-            bl = np.tan(np.pi/8) * 4/3 * radius
+            bl = np.tan(angle/4*np.pi) * 4/3 
             v_cone = np.array([(+0.0, +0.0), 
-            (-sin_ang*radius, -cos_ang*radius), 
-            (-sin_ang*radius + -cos_ang*bl, -cos_ang*radius + sin_ang*bl), 
-            (sin_ang*radius + cos_ang*bl, -cos_ang*radius + sin_ang*bl), 
-            (sin_ang*radius, -cos_ang*radius), 
+            (-sin_ang*radius, cos_ang*radius), 
+            (-sin_ang*radius + cos_ang*bl, cos_ang*radius + sin_ang*bl), 
+            (sin_ang*radius - cos_ang*bl, cos_ang*radius + sin_ang*bl), 
+            (sin_ang*radius, cos_ang*radius), 
             (0,0)])
             c_cone = np.array([Path.MOVETO, Path.LINETO, Path.CURVE4, Path.CURVE4, Path.CURVE4, Path.CLOSEPOLY]) 
             self._base_vertices_cone = np.tile(v_cone.reshape(-1),n).reshape(n, len(v_cone), 2)
@@ -237,7 +237,7 @@ def parse_kwargs(args):
 if __name__ == '__main__':
 
     parser = argparse.ArgumentParser()
-    parser.add_argument("--angle", "-a", help="Boid field of Vision [deg], default="+str(defaults["angle"]), type=float, default=defaults["angle"])
+    parser.add_argument("--angle", "-a", help="Boid field of Vision [rad], default="+str(defaults["angle"]), type=float, default=defaults["angle"])
     parser.add_argument("-v", help="Velocity, default="+str(defaults["v"]), type=float, default=defaults["v"])
     parser.add_argument("--width", help="Range for x-coordinate, default="+str(defaults["width"]), type=float, default=defaults["width"])
     parser.add_argument("--height", help="Range for y-coordinate, default="+str(defaults["height"]),type=float, default=defaults["height"])

### 2017-12-17 tex/article.tex

@@
 To determine the critical noise parameter $\eta_c$ we used a quadratic fit model
-to to fit the falling curve for $\eta < \eta_c$ and a linear fit for $\eta > 
+to fit the falling curve for $\eta < \eta_c$ and a linear fit for $\eta > 
 \eta_c$, both visible in figure~\ref{fig:va_over_eta}. $\eta_c$ is then set to 
